---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE, message = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Evaluation of Competing Risks Prediction Models using Polytomous Discrimination Index

<!-- badges: start -->
<!-- badges: end -->

For competing risks data, it is often important to predict a patient's outcome status at a clinically meaningful time point after incorporating the informative censoring due to competing risks. This can be done by adopting a regression model that relates the cumulative incidence probabilities to a set of covariates. To assess the performance of the resulting prediction tool, we propose an estimator of the polytomous discrimination index applicable to competing risks data, which can quantify a prognostic model's ability to discriminate among subjects from different outcome groups. The proposed estimator allows the prediction model to be subject to model misspecification and enjoys desirable asymptotic properties. We also develop an efficient computation algorithm that features a computational complexity of $O(n \log n)$. A perturbation resampling scheme is developed to achieve consistent variance estimation. Numerical results suggest that the estimator performs well under realistic sample sizes. We apply the proposed methods to a study of monoclonal gammopathy of undetermined significance. [1]

## Installation

You can install the development version of CRPDI like so:

```r
library(devtools)
install_github("lilyxj91/CRPDI",force = TRUE)
```

## Example

This is a basic example of computing PDI with competing risks data using Fine-Gray model.

```{r example}
library(CRPDI)
data(example_data)
n_l = 3  # number of outcome categories
tau = 1.4 # prespecified time for prediction

PDIs = fine_gray_pdi( dat=example_data, tau=tau, n_l=n_l, seed=1, cv_rep=3, zcov=c("z1","z2") )
PDIs
```

## Reference

[1] Ding, M., Ning, J., & Li, R.. (2020). Evaluation of competing risks prediction models using polytomous discrimination index. Canadian Journal of Statistics. https://doi.org/10.1002/cjs.11583
